---
title: "Lab 5"
author: "Sachiko Lamen"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide
---

Cool customization in the YAML ^^ (go to settings pinwheel in R, click output options) To give user option to see code if they want to use `code_folding`

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message= FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```


## Part 1: Confidence Intervals
 IN this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1

Create a single mock sample containing a number of values. Then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too. 

```{r}
# Create a mock sample

otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29) # Assuming some normality exists here, we can calculate a confidence interval using t distribution that takes into account sample size and greater uncertainty

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)
# most of the information returned is meaningless because the default is testing the null hypothesis that the mean otter length is equal to 0. (df = n-1). BUT, 95% confidence interval [29.07792, 44.67208]

# If we took multiple samples from the population and calculated a 95% confidence interval for each of them, we would expect that 95% of calculated confidence intervals to contain the true mean within the parameter. 

# find the standard deviation
otter_sd <- sd(otter_lengths)
```
Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches. (dont want to manually copy and paste like this. Find a way to tie the values in with in line referencing! - see below)

#### Now, using in-line referencing
(Use `objectname$valuename` to pull element values, hover over and press Cmd + Return to view value)

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`]

## Part 2: Two Sample T-Test

### Example 1

Make two mock samples, and ask the question: Do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean?
```{r}
# Make my mock samples

oak_trees <- c(20, 19, 24, 28, 34, 12, 15, 25)
  
  
pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two-sample T test
tree_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: Mean heights are the same
# i.e.: Trees are drawn from populations with the same mean height

```
Null hypothesis: Trees are drawn from populations with the same mean height

If these are samples taken from populations with the same mean height, there is a 28.7% chance of taking random samples from each populations  and finding that the sample means are at least as different as the means of the t-test. This is not sufficient evidence to reject the null hypothesis.

The mean heights of oak and pine trees were (x +- y) and (x +-y), respectively, and the difference was not significant (t(`r round(tree_t$parameter, 2)`) = `r round(tree_t$statistic, 2)`, p = `r round(tree_t$p.value,2)`))

"two sample t test notation: t(df) = t-statistic, p = p-value"

*AVOID*: p = 0

When things get really small (usually p<0.001)

*Not great:* p = 0.000000013
*Better:* p < 0.001


## Part 3: Another T test with cars data
Using the `mpg` dataset

### Take a look at the data

```{r}
compact_suv <- mpg %>%
  filter(class %in% c("compact", "suv")) # keep rows that contain compact or suv within the column `class`

# check for remaining levels
unique(compact_suv$class)

```
Create a histogram of city gas mileage (cty) faceted by class starting from compact_suv

```{r}
ggplot(data = compact_suv, x = cty) +
  geom_histogram(aes(color = class, x = cty), bins = 10) +
  facet_wrap(~ class) +
  labs (x = "City (mpg)",
        y = "Number of Cars")

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)
# if qq plot is linear then you can assume data is normally distributed.
```

Find some summary statistics for each group.

```{r}
car_stats <- compact_suv %>%
  group_by(class) %>%
  summarize(mean_city = round(mean(cty)),
            sd_city = sd(cty),
            sample_size = n())

car_stats
```

The `t.test()` function REALLY wants vectors of things. Here is how you pull data to put into a vector:Use `pull()` function to pull out a vector from a data frame

```{r}
compact_sample <- compact_suv %>%
  filter(class == "compact") %>%
  pull(cty)

# Your turn, do the same thing to get a vector of city gas mielages for SUVs

suv_sample <- compact_suv %>%
  filter(class == "suv") %>%
  pull(cty)
```

Null hypothesis (H0): Mean city gas mileages for SUVs and compact cars are the same

```{r}
t.test(compact_sample, suv_sample)
```
Conclusion: reject the null hypothesis that the mean gas mileages are the same. There is a significant differenc in mean city gas mileage for SUVs and compact cars (t(df) = t-statistic, p < 0.001)
















